Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-02-11 supplement.tex
Better layout

For theoreticians:

\itemize{
  \item subsection \ref{subsec:main_example}: extra figures and
    diagnostics regarding the main example.
  \item subsection \ref{subsec:distribution}: the result of using 
    multiple trees, as generated by the
    same stochastic process as the main example
}

For empiricists:

\itemize{
  \item subsection \ref{subsec:n_taxa}: the effect of the number
    of taxa
  \item subsection \ref{subsec:n_nucleotides}: the effect of the DNA
    alignment sequence length
  \item subsection \ref{subsec:non_clock}: the effect when the alignment
    is generated by a non-clock like nucleotide substitution model
  \item subsection \ref{subsec:simplest_correct_parameterization} shows the
    effect when doing an inference in the simplest use case
  \item subsection \ref{subsec:under_parameterization} shows the
    effect when doing an inference with an under-parameterization
  \item subsection \ref{subsec:better_label_needed} shows 
    \richel{better description needed}

}

>>>>

\itemize{
  \item{
    subsection \ref{subsec:main_example}: extra figures and
    diagnostics regarding the main example.
  }
  \item{
    subsection \ref{subsec:distribution}: the result of using 
    multiple trees, as generated by the
    same stochastic process as the main example
  }
  \item{
    subsection \ref{subsec:n_taxa}: the effect of the number
    of taxa
  }
  \item{
    subsection \ref{subsec:n_nucleotides}: the effect of the DNA
    alignment sequence length
  }
  \item{
    subsection \ref{subsec:non_clock}: the effect when the alignment
    is generated by a non-clock like nucleotide substitution model
  }
  \item{
    subsection \ref{subsec:simplest_correct_parameterization} shows the
    effect when doing an inference in the simplest use case
  }
  \item{
    subsection \ref{subsec:under_parameterization} shows the
    effect when doing an inference with an under-parameterization
  }
  \item{
    subsection \ref{subsec:better_label_needed} shows 
    \richel{better description needed}
  }
}
